RELIKE: Reionization Effective Likelihood from Planck 2018 Data

### 2021-04-28 paper/rei.tex
Updated paper/ to mirror latest arxiv submission (v1) + additionally restored Allison et al. reference; moved intermediate plots to results/plots_during_paper_writing/;

\end{abstract}
\pacs{}

@@

The cosmic microwave background (CMB) has helped establish the $\Lambda$CDM model as the standard cosmological model~\cite{Aghanim:2018eyx}. While many components of this standard cosmology model are well-understood, the details of the process of reionization however, remains one of the most uncertain pieces (see e.g.~\cite{2016ASSL..423.....M} and references therein).  It is usually characterized by a single parameter, the total Thomson optical depth, whose  uncertainty propagates into the inferences of other important parameters such as the primordial power spectrum amplitude. Through it, the uncertainty in reionization will become one of the major sources of uncertainty for measuring the sum of neutrino masses from future gravitational lensing measurements of the CMB~ \cite{Smith:2006nk,Allison:2015qca}; and will also have implications for inferring cosmic acceleration through the growth of structure~\cite{Hu:2003pt}.

>>>>

\end{abstract}
%\pacs{}

@@

The cosmic microwave background (CMB) has helped establish the $\Lambda$CDM model as the standard cosmological model~\cite{Aghanim:2018eyx}. While many components of this standard cosmology model are well-understood, the details of the process of reionization however, remains one of the most uncertain pieces (see e.g.~\cite{2016ASSL..423.....M} and references therein).  It is usually characterized by a single parameter, the total Thomson optical depth, whose  uncertainty propagates into the inferences of other important parameters such as the primordial power spectrum amplitude. Through it, the uncertainty in reionization will become one of the major sources of uncertainty for measuring the sum of neutrino masses from future gravitational lensing measurements of the CMB~ \cite{Smith:2006nk, Allison:2015qca} and will also have implications for inferring cosmic acceleration through the growth of structure~\cite{Hu:2003pt}.
